\textls[-0]{\thetitle}

### 2023-03-03 metatheory-condensed.tex
Make things more concise.

\item
\TT also features \emph{linkage transformers} modeling the inductive
construction of families from other families.
They allow a linkage to be created by inheriting or
overriding components of an existing linkage, or by extending an existing
linkage with new components.

\item
Inductive types are modeled as W-types~\cite{martin1984intuitionistic} and their
extension as overriding.

@@

@@

>>>>

\item
\TT also features \emph{linkage transformers}, used to model the features like inheritance, extending and overriding components in \Lang .
\item
Inductive types are modeled as W-types~\cite{martin1984intuitionistic} and their
extension as overriding.

@@

% TODO: Remove mentioning conventional Wtype here

@@

% Add example for representing tm here
